Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-19 paper/main.tex
wip
bold font for PL exprs
elan on vars, bold if-then-else

\usepackage{booktabs}
\usepackage{mdframed}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\newcommand{\getsr}{\xleftarrow{\$}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\ift}[3]{\mathrm{if} \; #1 \; \mathrm{then} \; #2 \; \mathrm{else} \; #3}

\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclareMathOperator{\Ber}{\mathrm{Ber}}
\DeclareMathOperator{\prob}{\mathcal P}
\DeclareMathOperator{\expect}{\mathrm{E}}
\DeclareMathOperator{\indicat}{\mathrm{I}}
\DeclareMathOperator{\bigo}{\mathcal O}
%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

@@

@@

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
%\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional

>>>>

\usepackage{booktabs}
\usepackage{mdframed}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\newcommand{\getsr}{\xleftarrow{\$}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\ift}[3]{\mathbf{if} \; #1 \; \mathbf{then} \; #2 \; \mathbf{else} \; #3}
\newcommand{\integral}[3]{\int_{#1} \! #2 \, \mathrm{d} #3}
\newcommand{\isaprob}[3]{\isa{\isasymP{\isacharparenleft}#1 \isatext{in} #2{\isachardot} #3\isacharparenright}}

\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclareMathOperator{\Rnonneg}{\mathbb R_{\geq 0}}
\DeclareMathOperator{\Ber}{\mathrm{Ber}}
\DeclareMathOperator{\prob}{\mathcal P}
\DeclareMathOperator{\expect}{\mathrm{E}}
\DeclareMathOperator{\indicat}{\mathrm{I}}
\DeclareMathOperator{\bigo}{\mathcal O}
%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

@@

% TODO: put in everyone's names here

\author{Yong Kiam Tan}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
% \author{Seng Joe Watt}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}

@@

\supplement{TODO}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
% AFP entry
\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
% Zenodo code repo
\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
